Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-05-01 tex/paper1/paper1.tex
nicer plots for the main fit results, and edits to the paper

\documentclass[manuscript]{../aastex52/aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

\begin{figure}
\label{fig:dist171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.}
\end{figure}

@@

\begin{figure}
\label{fig:fit171}
\plottwo{}{}
\plottwo{}{}
\caption{}
\end{figure}

\begin{figure}
\label{fig:fit193}
\plottwo{}{}
\plottwo{}{}

\caption{}
\end{figure}

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
P_{0}(f) = Af^{-n} + C,
\end{equation}
where $A>0$ is a proportionality constant and $n>0$ is the power law
index.  The quantity $C>0$ models the high-frequency / low power end
of the spectrum where the detection properties of the detector
apparatus are assumed to dominate the observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model for these regions
should be considered.  The spectrum $P_{1}$ where
\begin{equation}
\label{eq:pwrlawbump}
P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus a second term which
models any power over and above the power law.

Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the best fit results of
each model to the data (for details on the fitting procedure, see
Section \ref{sec:app:ind}).

@@

Figures \ref{} show that the logarithm of the Fourier power in a
region of the Sun may be approximated by a normal distribution $N(\mu,
\sigma)$.  The
maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
\label{eqn:mlmean}
where $N$ is the number of independent measurements.  The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}

>>>>

\documentclass[preprint]{../aastex52/aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

\begin{figure}
\label{fig:dist171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.)}
\end{figure}

@@

\begin{figure}
\label{fig:fit171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
\caption{aaa}
\end{figure}

%\begin{figure}
%\label{fig:fit193}
%\plottwo{}{}
%\plottwo{}{}
%
%\caption{}
%\end{figure}
\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\sigma$}
}
\startdata
loop footpoints & 171\AA  & $0.47^{+0.01}_{-0.01}$  &$1.86^{+0.01}_{-0.01}$  & $-3.97^{+0.00}_{-0.00}$  & $-1.333^{0.02}_{-0.02}$ & $1.05^{+0.02}_{-0.02}$  & $0.31^{+0.03}_{-0.03}$  \\
                & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\

moss            & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\

quiet Sun       & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\

sunspot         & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\end{deluxetable}

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $A>0$ is a proportionality constant and $n>0$ is the power law
index.  The quantity $C>0$ models the high-frequency / low power end
of the spectrum where the detection properties of the detector
apparatus are assumed to dominate the observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model $M_{2}$ for these
regions should be considered.  The second model $M_{2}$ has two
contributions to the overall \Fps; a background power-law of the form
of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
model is given by
\begin{equation}
\label{eq:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the best fit results of
each model to the data (for details on the fitting procedure, see
Section \ref{sec:app:ind}).

@@

Figures \ref{} show that the logarithm of the Fourier power in a
region of the Sun may be approximated by a normal distribution $N(\mu,
\sigma)$.  The
maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
\label{eqn:mlmean}
\end{equation}
where $N$ is the number of independent measurements.  The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}
